Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-04 PaperVictor.tex
Finish revision.

\notaL{Tengo los mismos comentarios que para la figura previa.}
Fig \ref{Fig3}(b) shows $\braket{R}$ for
different values of $\alpha$ and $N_{p}$. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. \notaL{No debería ser el mismísimo máximo y no
  nada más en la zona?} The reflectance calculation  is
shown in Fig. \ref{Fig3}(c).  This structure
has a wide quasi-omnidirectional gap with $R(\lambda,\theta)>0.95$
with $\lambda$ from 850 to 3000 nm and $\theta$ from
$0^\circ$ to $70^\circ$.\notaL{Me da la impresión que confundías
  promedio con reflectancia} The measured and calculated reflectance
are compared  for several angles in Fig \ref{Fig3}(d). The synthesized PS
multilayered 1D photonic structure behaves as a quasi omnidirectional
mirror for $0^\circ\le\theta\le 60^\circ$ with a bandwidth of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth,\notaL{No entiendo:
  está diseñada para tener un gradiente de ancho. Te refieres a un
  gradiente adicional al diseñado?} which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and
interface roughness \notaL{No se entiende si este es otro efecto o si
  la rugosidad produce un gradiente de anchos}.

\subsection{Photonic structure with sub-mirrors stacking}

Another technique to design Bragg mirrors in a wide range of the
electromagnetic spectrum is by stacking sub-mirrors at different
wavelengths \cite{DelRio2018,Agarwal2003}. Such grouping must meet the condition
imposed by the dispersion relation, $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
the period, which corresponds to the actual thickness of the sub-mirror, $\pm K$
represents a 1D Bloch's vector corresponding to a wave that propagates along
$z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the
trace. This equation is bounded by the minimum and maximum values that the cosine
function can take. Furthermore, if  the value of $\left\vert \text{Tr}\left(
M\right) \right\vert$ is $>2$, it indicates that this frequency will not
be able to propagate through the structure.

The ideal stack of sub-mirrors would be that PBG of the $j$-th mirror begins
at the edge of the PBG of the $j-1$-th mirror, until the desired interval has been
covered. However, this arrangement does not give the maximum average reflectance due to
the decrease in the reflectance at each intersection of the two PBGs. On the other hand,
the number of periods of each sub-mirror is an important parameter due to its direct
dependence on the magnitude and  width of  the photonic band gap.  As the structures
were synthesized using porous silicon, it is essential to minimize the number of
periods corresponding to the visible region sub-mirrors. Also, in the supplementary
information we show the reflectance calculations for structures composed of sub
mirrors with a constant number of periods, in these cases ODBMs are not obtained.
For these reasons, the number of periods for each mirror was chosen as follows: for
design wavelengths less than 500 nm ($\lambda_{D}<$500 nm), one period, for 500
$<\lambda_{D}<$650 nm, two periods , for 650 $<\lambda_{D}<$800 nm, three, and for
$\lambda_{D}>$ 800 nm, the number of periods was variable (Fig. \ref{Fig4}(a)).
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F6OptimizedNIRSE.pdf}
\end{center}
\caption{(a) Diagram showing the distribution of sub-mirrors and the corresponding
number of periods in a PS multilayer. (b) Maximization of the average reflectance as
a function of the overlap photonic band gap for the structures formed by sub-mirrors
with a fixed number of periods (3 and 4), and for structures with the design of (a)
using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$ nm. (c) Mapping the
calculated reflectance of the designed structure with the optimized values for non
polarized light. (d) Comparison of reflectance spectra calculated and measured at
different angles of incidence. The gray band indicates the region in which the
reflectance is greater than 95$\%$. Inset shows the top view photograph of the
synthesized structure.}
\label{Fig4}
\end{figure}

Therefore, in this work the overlap percentage of the PBGs of the first and second
mirror, second and third mirror, and so on, is also optimized. Fig \ref{Fig4}(b)
shows the optimization results in terms of maximum average reflectance with respect
to the PBG overlap at different sub-mirror periods, keeping them fixed (3, 4) or
variable (1, 2  and 3) for $\lambda<500$(1 period), $500<\lambda<650$ nm (2
periods), $650<\lambda<800$ nm (3 periods) and $\lambda>800$ (3, 6 periods). For
example, the calculations corresponding to the reflectance spectra of the structures
formed using sub-mirrors with constant periods (3 and 4) revealed a lower average
reflectance as compared to the structure formed with variable periods. The 1D
photonic structure with the highest average reflectance (named as ST-C)  is the one
designed with variable periods and contemplates 6 periods for each sub-mirror in the
NIR region. In the optimized structure designed for 400-3000 nm range, the photonic
band gap overlap is around 78$\%$, thickness is 41.5 $\mu $m and the average
reflectance is 95.3$\%$, when the  electromagnetic waves are incident from
0${{}^\circ}$ to 89 ${{}^\circ}$. The optimized photonic structure is made up of 18
sub-mirrors tuned to the following wavelengths 400, 460, 510, 570, 640, 720,810,
910, 1020, 1150, 1290, 1450, 1630, 1830, 2060, 2320, 2610 and 2860 nm  with periods
of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and above).

The reflectance mapping shown in Fig \ref{Fig4}(c) reveals a quasi omnidirectional
band gap from 950 to 2900 nm, taking into account 0${{}^\circ}$ to 60${{}^\circ}$ of
incidence. It is also observed that at incidence angles $>$70${{}^\circ}$, for long
wavelengths the reflectance decreases and has oscillations, which are attributed to
the greater penetration of the electromagnetic field within the structure, as shown
by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in supplementary
information we show the transfer matrix trace calculations as a function of the
wavelength and the incidence angle for the ST-C photonic structure using the TE and
TM polarization. In Fig \ref{Fig4}(d) the calculated and measured reflectance
corresponding to the structure ST-C, at different angles of incidence is compared.
Although, the quasi omnidirectional band gap of the synthesized structure is
slightly less than that calculated (located from 950 to 2750 nm), the measured PBG
is almost twice as compared to the recently reported similar structures
(\cite{DelRio2018,Chavez2020}).

Finally, table 2 shows some porous silicon based ODBMs designed to operate in the
NIR region and the width of the omnidirectional band gap is compared with the
structures analyzed in the present study. The table reveals that the porous silicon
based structures ST-B and ST-C have the widest gap width, being 1.8 times greater
than recently reported works.

@@

We have demonstrated the formation of highly reflective PS multilayer photonic
structures optimized using two types of design techniques for maximal reflectance
and minimal thickness in the NIR region. With \textit{chirped}-type Bragg mirrors,
two regions of the electromagnetic spectrum were analyzed. The first region (350nm -
1400 nm), optimized through an increasing function resulted in an average
reflectance $>85\%$ with the quasi omnidirectional PBG of 360 nm centered at 1160 nm
(980-1340 nm) for the angular range 0-60${{}^\circ}$ and more than 50$\%$ of
reflectance from 550-980nm. The second structure was designed for 850-3000 nm
wavelength range and the synthesized structure with optimized parameters resulted in
the average reflectance of $~91\%$ with q-OD bandgap from 980 to 2780 nm and a
thickness of 60.4 $\mu$m. The other design technique consisting of sub-mirrors
stacks (designed at different wavelengths), was optimized for maximum average
reflectance with respect to the percentage overlap of the PBG for each sub-mirror. A
multilayer structure using the optimized parameters with sub-mirrors stack method
was obtained with the average reflectance of $~95\%$ and a thickness of 41.5 $\mu$m.
Furthermore, this structure revealed a 1800 nm q-OD PBG, centered at 1850 nm, in
angular range 0-60${{}^\circ}$. Therefore, this second technique was found to be
better due to the decreased thickness (by a factor of $~1.5$) of the framework and
increased average reflectance. Additionally, the analysis techniques developed here
can be used to optimize reflectance with other refractive index contrasts in PS
multilayers or different other systems composed of other types of materials. Such
proposed structures could be used as mirrors for solar concentrators, flat focusing
reflectors, thermal regulators, or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.

>>>>

\notaL{Tengo los mismos comentarios que para la figura previa.}
Fig \ref{Fig3}(b) shows $\braket{R}$ for
different values of $\alpha$ and $N_{p}$. As in the
previous case, the optimized parameters are within the zone of maximum
average reflectance. \notaL{No debería ser el mismísimo máximo y no
  nada más en la zona?} The reflectance calculation  is
shown in Fig. \ref{Fig3}(c).  This structure
has a wide quasi-omnidirectional gap with $R(\lambda,\theta)>0.95$
with $\lambda$ from 850 to 3000 nm and $\theta$ from
$0^\circ$ to $70^\circ$.\notaL{Me da la impresión que confundías
  promedio con reflectancia} The measured and calculated reflectance
are compared  for several angles in Fig \ref{Fig3}(d). The synthesized PS
multilayered 1D photonic structure behaves as a quasi omnidirectional
mirror for $0^\circ\le\theta\le 60^\circ$ with a bandwidth of approximately 1800 nm. The difference
between the calculated and measured spectra at the longer wavelengths can be
attributed to a thickness gradient along the depth,\notaL{No entiendo:
  está diseñada para tener un gradiente de ancho. Te refieres a un
  gradiente adicional al diseñado?} which is more pronounced in
the lower layers due to the restricted diffusivity of the electrolyte
through the structure itself \cite{Negro2003,Vincent1993} and
interface roughness \notaL{No se entiende si este es otro efecto o si
  la rugosidad produce un gradiente de anchos}.
y
\subsection{Photonic structure with sub-mirrors stacking}\label{ss:stacked}

Another technique to design Bragg mirrors in a wide range of the
electromagnetic spectrum is by stacking sub-mirrors tuned to different
wavelengths \cite{DelRio2018,Agarwal2003}. Such grouping must meet the condition
imposed by the dispersion relation,\notaL{No se entiende, ¿de qué la gira
la relación de dispersión? Es la relación de dispersión ¿de qué? Falta
una explicación!} $\cos KD=\frac{1}{2}\text{Tr}\,M$, where $D$ is
the period, which corresponds to the actual thickness of the
sub-mirror\notaL{Por qué? El espejo podría tener varios periodos.}, $\pm K$
represents a 1D Bloch's vector corresponding to a wave that propagates along
the $z$-direction \cite{Mochan1987,Mochan1988,Perez2018}, and T$\text{r}$ denotes the
trace. This equation is bounded by the minimum and maximum values that the cosine
function can take. Furthermore, if  the value of $\left\vert \text{Tr}\left(
M\right) \right\vert$ is $>2$, it indicates that this frequency will not
be able to propagate through the structure. \notaL{Las ideas están
  bien, pero está muy mal explicado, en desorden}

The ideal stack of sub-mirrors would be that edge where the PBG of the $j$-th mirror begins
is close to the  edge of the where the PBG of the $j-1$-th mirror
ends, and sufficient mirrors are stacked until the desired interval
bandwidth has been
covered. However, this arrangement does not give the maximum average reflectance due to
the decrease in the reflectance at each intersection of the two
PBGs.\notaL{QUé es una intersección de PBG? Escribe para que el lector
  entienda} On the other hand,
the number of periods of each sub-mirror is an important parameter due to its direct
dependence on the magnitude and  width of  the photonic band gap.  As the structures
were synthesized using porous silicon, it is essential to minimize the number of
periods corresponding to the visible region sub-mirrors. Also, in the supplementary
information we show the reflectance calculations for structures composed of sub
mirrors with a constant number of periods, in these cases ODBMs are not obtained.
For these reasons, the number of periods for each mirror was chosen as follows: for
design wavelengths less than 500 nm ($\lambda_{D}<$500 nm), one period, for 500
$<\lambda_{D}<$650 nm, two periods , for 650 $<\lambda_{D}<$800 nm, three, and for
$\lambda_{D}>$ 800 nm, the number of periods was variable
(Fig. \ref{Fig4}(a)). \notaL{No entendí el argumento, ni cómo
  dterminaste para qué lambdas se usan tantos o cuántos periodos. ¿Fue
  prueba y error? ¿Fue una optimización?}\notaL{Por cierto,
  ¿optimizaste qué tanto traslapar espectros sucesivos o usaste la
  regla de que se toquen los bordes de banda?}
\begin{figure}[tbph]
\begin{center}
\includegraphics[width=\textwidth]
{F6OptimizedNIRSE.pdf}
\end{center}
\caption{\notaL{Stack, no stak. ¿Qué significa la región rugosa que
    rodea la estructura?} (a) Diagram showing the distribution
  of sub-mirrors and the corresponding
number of periods in a PS multilayer.\notaL{Esto no es un cartel. No
  entiendo qué pretende ilustrar el panel (a)} (b) Maximization of the average reflectance as
a function of the overlap photonic band gap for the structures formed by sub-mirrors
with a fixed number of periods \notaL{No has explicado a qué te
  refieres con esta optimización. No has explicado qué es el overlap
  photonic band gap. Esto parece tomado de un cartel, pero el artículo
debe ser autocontenido; no estás ahí parado para explicar.}(3 and 4),
and for structures with the design of (a)
using 3 and 6 periods for the tuned sub-mirrors in $\lambda>800$
nm.\notaL{No entendí nada.} (c)
Calculated reflectance for the optimized structure for non
polarized light. (d) Comparison between the measured and calculated
reflectance spectra at several angles of incidence. The gray band indicates the region in which the
reflectance is greater than 95$\%$. Inset shows a photograph with a top view of the
synthesized structure.}
\label{Fig4}
\end{figure}

Therefore, in this work the overlap percentage of the PBGs of the first and second
mirror, second and third mirror, and so on, is also optimized. Fig \ref{Fig4}(b)
shows the optimization results in terms of maximum average reflectance with respect
to the PBG overlap at different sub-mirror periods, keeping them fixed (3, 4) or
variable (1, 2  and 3) for $\lambda<500$(1 period), $500<\lambda<650$ nm (2
periods), $650<\lambda<800$ nm (3 periods) and $\lambda>800$ (3, 6 periods). For
example, the calculations corresponding to the reflectance spectra of the structures
formed using sub-mirrors with constant periods (3 and 4) revealed a lower average
reflectance as compared to the structure formed with variable periods. The 1D
photonic structure with the highest average reflectance (named as ST-C)  is the one
designed with variable periods and contemplates 6 periods for each sub-mirror in the
NIR region. In the optimized structure designed for 400-3000 nm range, the photonic
band gap overlap is around 78$\%$, thickness is 41.5 $\mu $m and the average
reflectance is 95.3$\%$, when the  electromagnetic waves are incident from
0${{}^\circ}$ to 89 ${{}^\circ}$. The optimized photonic structure is made up of 18
sub-mirrors tuned to the following wavelengths 400, 460, 510, 570, 640, 720,810,
910, 1020, 1150, 1290, 1450, 1630, 1830, 2060, 2320, 2610 and 2860 nm  with periods
of 1 (400, 460 nm), 2(510, 570, 640 nm), 3 (720 nm) and 6 (810 nm and
above).\notaL{Sugiero reescribir tratando de que la explicación sea clara}

The reflectance mapping shown in Fig \ref{Fig4}(c) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, for $\theta$ between
$0^\circ$ and $60^\circ$. It is also observed that at incidence angles $>$70${{}^\circ}$, for long
wavelengths the reflectance decreases and has oscillations, which are attributed to
the greater penetration of the electromagnetic field within the structure, as shown
by Puente-D\'{\i}az, et al \cite{Puente2020}. Furthermore, in the supplementary
information we show the trace of the transfer matrix as function of the
wavelength and the incidence angle for the ST-C photonic structure for TE and
TM polarizations.\notaL{¿Para qué ponemos esta información
  suplementaria? ¿Qué aprenderá el lector de ella?} In Fig
\ref{Fig4}(d) we compare the calculated and measured reflectance
for the structure ST-C, at several angles of incidence.
Although, the quasi omnidirectional wavelength range of the synthesized structure is
slightly smaller than the calculated one, from 950 to 2750 nm, the measured PBG
is almost twice as wide as those of recently reported similar structures
(\cite{DelRio2018,Chavez2020}).

Finally, table 2 shows some porous silicon based ODBMs \notaL{Me
  preocupa un poco la nomenclatura: si no son periódicos, ¿son espejos
  de Bragg?} designed to operate in the
NIR region and the width of the omnidirectional band gap is compared with the
structures analyzed in the present study. The table reveals that the porous silicon
based structures ST-B and ST-C have the widest gap width, being 1.8 times greater
than recently reported works.\notaL{Es justa la comparación? Ellos
  estaban tratando de hacer un espejo de espectro muy amplio y no
  pudieron hacerlo tan ancho como nosotros o simplemente estaban
  haciendo otra cosa?}

@@

We have designed, fabricated and characterized highly reflective PS multilayer photonic
structures with a wide spectral range, optimized using two techniques for maximal reflectance
and minimal thickness in the NIR region \notaL{Parte del trabajo no
  fue NIR.} With \textit{chirped}-type
Bragg\notaL{Tengo la duda sobre llamarles Bragg} mirrors,
two regions of the electromagnetic spectrum were analyzed. The first region (350nm -
1400 nm), optimized through an increasing function resulted in a
reflectance $R>0.85$ with a range of 360 nm centered at 1160 nm
(980-1340 nm) for the angular range $0-60^\circ$ and $R>0.50$ of
reflectance from 550-980nm. The second structure was designed for a
wavelength range from 850-3000 nm
and the synthesized structure with optimized parameters resulted in
the average reflectance of $~91\%$ with q-OD \notaL{No definiste q-OD
  nunca} bandgap from 980 to 2780 nm and a
thickness of 60.4 $\mu$m. The other design technique consists of
stacking sub-mirrors
tuned to different wavelengths, and was optimized for a maximum average
reflectance using  the overlap of the gap of succesive sub-mirrors as
the optimization parameter. We obtained
a reflectance $R>0.95$ and a thickness of 41.5 $\mu$m within a
wavelength range of 1800 nm centered at 1850 nm, with  an
angular range $0-60^\circ$. Therefore, we found this second technique to be
better as it yields thinner structures by a factor of $~1.5$ and
increased average reflectance. Additionally, the analysis techniques developed here
can be used to optimize reflectance with other refractive index contrasts in PS
multilayers or in systems composed of other types of materials. Such
proposed structures could be used as mirrors for solar concentrators, flat focusing
reflectors, thermal regulators, or, if defects are included, as filters or remote
chemical/biosensors with a wide angular independent response.
